### 2020-05-07 README.Rmd
added github actions
added lifecycle badge

@@

```
install.packages("devtools")
```

@@

```
devtools::install_github("https://github.com/AIMS/data-platform-r")
```

>>>>

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/AIMS/data-platform-r/workflows/R-CMD-check/badge.svg)](https://github.com/AIMS/data-platform-r/actions)
<!-- badges: end -->

@@

```{r, eval = FALSE}
install.packages("devtools")
```

@@

```{r, eval = FALSE}
devtools::install_github("https://github.com/AIMS/data-platform-r")
```
